Macro Impacts

### 2016-09-11 LaTeX/Old/Macro Impacts Revised.tex
Updated Organization

The equation governing the evolution of the temperature field in 2 dimensions is, with no driving term,
\begin{align}
\partial_t T - \alpha\nabla^2 T = 0
\end{align}
where $\alpha$ is the thermal diffusivity, and $\alpha=\f{k}{c_p\rho}$. In cylindrical coordinates and for $T = T(r)$, we have
\begin{align}
\partial_t T - \alpha\nabla_r T = 0
\end{align}
We now Fourier transform in $r$ and $\phi$, yielding
\begin{align}
\partial_t\tilde T =-\alpha k_r^2 \tilde T\,,
\end{align}
where
\begin{align}
\tilde T =  \int_0^\infty r \diff r\int_{0}^{2\pi} T e^{i r(k_x\cos\phi +k_y\sin\phi)}\diff \phi\, = 2\pi \int_0^\infty r \diff r  T J_0(k_r r)\,.
\end{align}
where
\begin{align}
k_r = \sqrt{k_x^2 +k_y^2}
\end{align}
Now, we integrate $\partial_t\tilde T =-\alpha k_r^2 \tilde T\,$ and find that
\begin{align}
\tilde T = C_1e^{-\alpha k_r^2 t}.
\end{align}

Consider the initial condition of a delta source along the z-axis in cylindrical coordinates:
\begin{align}
T(r,0) = \f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_X c_p}\delta(r),
\end{align}
Note that this model/initial condition is reasonable given that the delta source becomes a Gaussian with the same energy (assuming energy is conserved) an instant after the initial input of the delta source.

>>>>

The equation governing the evolution of the temperature field in 2 dimensions is, with no driving term,
\begin{align}
\partial_t T - \alpha\nabla^2 T = 0
\end{align}
where $\alpha$ is the thermal diffusivity, and $\alpha=\f{k}{c_p\rho}$ where k, $\rho$ and $c_p$ are the thermal conductivity, density and heat capacity of the impacted material respectively. In cylindrical coordinates and for $T = T(r)$, we have
\begin{align}
\partial_t T - \alpha\nabla_r T = 0
\end{align}
We now Fourier transform in $r$ and $\phi$, yielding
\begin{align}
\partial_t\tilde T =-\alpha k_r^2 \tilde T\,,
\end{align}
where
\begin{align}
\tilde T =  \int_0^\infty r \diff r\int_{0}^{2\pi} T e^{i r(k_x\cos\phi +k_y\sin\phi)}\diff \phi\, = 2\pi \int_0^\infty r \diff r  T J_0(k_r r)\,.
\end{align}
where
\begin{align}
k_r = \sqrt{k_x^2 +k_y^2}
\end{align}
Now, we integrate $\partial_t\tilde T =-\alpha k_r^2 \tilde T\,$ and find that
\begin{align}
\tilde T = C_1e^{-\alpha k_r^2 t}.
\end{align}

Consider the initial condition of a delta source along the z-axis in cylindrical coordinates:
\begin{align}
T(r,0) = \f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_X c_p}\delta(r),
\end{align}
where $\frac{dE}{dx}$,$r_X$,$\sigma_{X}$ are the energy deposition, radius and scattering cross section of the Macro respectively. Note that this model/initial condition is reasonable given that the delta source becomes a Gaussian with the same energy (assuming energy is conserved) an instant after the initial input of the delta source.
